### 2013-07-24 doc/asplos14/evaluation.tex
shrink two plots

The goal of our evaluation is to understand whether the core pieces of the \Grappa
runtime system, namely our tasking system and the global memory/communication
layer work as expected and whether together they are able to efficiently run irregular
applications. We evaluate \Grappa in three basic steps:

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/context_switch_time.pdf}
    \end{center}
    \caption{Average context switch time with and without prefetching.}
    \label{fig:context-switch-exp}
\end{figure}

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows with and without message aggregation.}
    \label{fig:grappa-gups}
\end{figure}

>>>>

The goal of our evaluation is to understand whether the core pieces of the \Grappa
runtime system, namely our tasking system and the global memory/communication
layer, work as expected and whether together they are able to efficiently run irregular
applications. We evaluate \Grappa in three basic steps:

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.4\textwidth]{figs/context_switch_time.pdf}
    \end{center}
    \caption{Average context switch time with and without prefetching.}
    \label{fig:context-switch-exp}
\end{figure}

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.4\textwidth]{figs/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows with and without message aggregation.}
    \label{fig:grappa-gups}
\end{figure}
